R-LIME: Rectangular Constraints and Optimization for Local Interpretable Model-agnostic Explanation Methods

### 2024-02-26 paper/paper.tex
Work on the paper

% settings for cleveref
\crefname{figure}{Fig.}{Figs.}
\crefname{table}{Table.}{Tables.}

@@

\section{Introduction}
Machine learning models, such as deep learning and random forests,
have been widely employed in various industrial applications
due to their significant improvement in accuracy in recent years.
However,
the increasing complexity and black-box nature of these models pose challenges,
particularly in critical decision-making scenarios like healthcare and finance,
where the opacity of decision process becomes a major obstacle to
implementation.
Consequently,
there has been extensive research in the field of post-hoc explanations
for machine learning models~\cite{%
	guidotti2018local,radulovic2023bella,ribeiro2016why,ribeiro2018anchors}.

Existing post-hoc explanation methods are categorized
into \emph{model-dependent} and \emph{model-agnostic} methods,
based on their dependence on the model's structure.
Furthermore, model-agnostic methods are classified into
\emph{global} and \emph{local} methods based on their locality in input space.
Local methods, in contrast, explain output of the model for a specific input
(focal point) in the vicinity of that input.
While local methods offer more simple and accurate explanations
than global methods,
the scope of the explanation is limited to the vicinity of the focus point.

This paper specifically focuses on \emph{local} \emph{model-agnostic} methods,
which do not rely on the models' structure
and explain the models' behavior in the vicinity of a specific input.
For instance, LIME (Local Interpretable Model-agnostic Explanations)
\cite{ribeiro2016why} approximates the complex model's decision boundary
locally using a simpler model around the given focal point.
Although LIME enables users to interpret the local behavior of complex models,
it does not explicitly provide the effective scope of the explanation
\cite{ribeiro2018anchors}.
This limitation can lead
users to overgeneralize the knowledge derived from the explanation.
Without a clear indication of the scope of the explanation,
users might mistakenly apply
the derived knowledge to instances outside this scope,
potentially leading to misunderstanding of the black-box model's behavior.

To address this limitation of LIME,
we propose a new method called R-LIME (Ruled LIME),
which interprets complex classifiers in an interpretable region.
R-LIME locally approximates a complex decision boundary linearly
in a rectangular region and maximizes the region
as long as the accuracy of the linear classifier is
higher than a specified threshold.
The resulting rectangular region is interpretable for users because it is
expressed as a conjunction of feature predicates (\cref{fig:example-rlime}).

\section{Related Work}
\begin{figure}[t]
	\centering
	\vspace{0.5cm}
	\begin{subfigure}[t]{0.55\textwidth}
		\centering
		\includegraphics[scale=0.35]{example-instance}
		\caption{Focal point.}\label{fig:example-instance}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{0.45\textwidth}
		\begin{subfigure}[t]{\textwidth}
			\centering
			\includegraphics[scale=0.35]{example-lime}
			\caption{%
				Explanation by LIME\@.
				It provides contributions of each feature to the output,
				but does not explicitly indicate its scope.
			}\label{fig:example-lime}
			\vspace{0.4cm}
		\end{subfigure}
		\begin{subfigure}[t]{\textwidth}
			\centering
			\includegraphics[scale=0.35]{example-anchor}
			\caption{%
				Explanation by Anchor.
				It provides the effective scope of the explanation,
				but does not show the influence of each feature.
			}\label{fig:example-anchor}
		\end{subfigure}
	\end{subfigure}
	\hspace{0.3cm}
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\vspace{-1.96cm}
		\includegraphics[scale=0.35]{example-rlime}
		\caption{%
			Explanation by R-LIME\@.
			It provides both contributions of each feature and
			its effective scope.
		}\label{fig:example-rlime}
	\end{subfigure}
	\caption{%
		Example of explanations by LIME, Anchor and R-LIME
		for a sentiment prediction model.
	}\label{fig:example}
\end{figure}
In this chapter,
we overview existing research on post-hoc explanations,
which explain the behavior of complex models already trained.
They are categorized
into \emph{model-dependent} and \emph{model-agnostic} methods
based on their dependence on the model's structure.

Model-dependent methods primarily focus on deep neural networks and
explain the models' behavior using their parameters~\cite{samek2021explaining}.
Layer-wise relevance propagation (LRP)~\cite{bach2015pixel} and
deep Taylor decomposition (DTD)~\cite{montavon2017explaining}
are representative model-dependent methods.
While these methods can provide detailed explanations
(e.g., layer-wise explanations for neural networks)
using the models' internal parameters,
it is often challenging
to apply the same method to models with different structures.

On the other hand,
model-agnostic methods
do not rely on the models' parameters and utilize only their output.
Although these methods are applicable to any model,
they cannot explain the reasoning process inside the model.
Furthermore, model-agnostic methods are classified into
\emph{global} and \emph{local} methods based on their locality in input space.
Global methods
aim to explain the model's behavior across the entire input space,
seeking explanations valid for any input.
Partial dependence plots (PDP)~\cite{friedman2001greedy} and
accumulated local effects (ALE)~\cite{apley2020visualizing}
are representative global methods.
However, providing global explanations becomes challenging
as the model's complexity increases.
Local methods, in contrast, explain output of the model for a specific input
(focal point) in the vicinity of that input.
While local methods offer more simple and accurate explanations
than global methods,
the scope of the explanation is limited to the vicinity of the focus point.

Model-dependent methods aim to explain the behavior of complex models
using their internal parameters.

@@

LIME provides valuable insights into the local behavior of the model
by showing the contribution of each feature to the output $f(x)$.
However, due to not explicitly indicating the perturbation region,
users cannot assess the effective scope of the explanation
\cite{ribeiro2018anchors}.
An example of explanation by LIME for a sentiment prediction model
is illustrated in \cref{fig:example-lime}.
The explanation provides suggests that
the word ``not'' mainly contributes to the positive prediction,
but does not explicitly indicate the effective scope.
Without the scope,
users might mistakenly apply the knowledge derived from the explanation
to other instances far from the focal point,
potentially leading to misunderstanding of the black-box model's behavior
\cite{ribeiro2018anchors}.
For example,
user may apply the insights derived from the explanation
(\cref{fig:example-lime})
to the sentence ``This book is not good.''
and mistakenly conclude that the word ``not''
mainly contributes to the positive prediction for this sentence as well,
which is incorrect obviously.

@@

While Anchor provides an effective scope of the explanation,
the information it includes is less than LIME,
limiting its utility~\cite{ribeiro2018anchors}.
An example of Anchor explanation for a sentiment prediction model
is illustrated in \cref{fig:example-anchor}.
The explanation suggests that changing words other than ``not'' and ``bad''
has little impact on the classifier's output.
While it clearly cannot be applied to the sentence ``This book is not good''
because of not including the word ``bad'',
the explanation does not provide details about the influence of each word,
resulting in less user insight into the model's behavior compared to LIME
(\cref{fig:example-lime}).

\subsection{Overview}
We propose R-LIME,
a method that aims to address the limitations of LIME~\cite{ribeiro2016why},
Anchor~\cite{ribeiro2018anchors} and BELLA \cite{radulovic2023bella}.
Our method locally approximates the given black-box classifier $f$
around the focal point $x$ by a linear classifier $g$ similar to LIME and BELLA,
but samples parturbation from a rectangular region similar to Anchor
so that the generality of approximation is explicitly provided
(\cref{fig:rlime}).
The accuracy of $g$ is defined as the "accuracy" of the rule,
and the generality of explanations is defined as the "coverage" of the rule.

Anchor maximizes the coverage of region $A$
as long as the probability of the output of the black-box classifier $f$ matching $f(x)$
within $A$ exceeds a given threshold $\tau$.
The proposed method, on the other hand, learns an linear classifier $g$
within the rectangular region $A$ and maximizes the coverage of $A$
under lower constraints on the accuracy of $g$.
We modify the Anchor's definition of accuracy in \cref{eq:anchor_def_prec}
as follows:
\begin{equation}
	\Prec(A)=\underset{g\in G}{\max}\ \mathbb{E}_{z\sim\mathcal{D}(z|A)}
	[\mathbbm{1}_{f(z)=g(z)}]. \label{eq:def_prec}
\end{equation}
where $G$ is the set of possible linear classifiers.
By solving the optimization problem in \cref{eq:main_problem}
under the modified accuracy definition in \cref{eq:def_prec},
we can select the rule that enables explanation with high accuracy and generality.
The characteristics of R-LIME are listed below:
\begin{itemize}
	\item The approximation region is optimal and interpretable.
	\item The dataset is not directly accessed, and only the distribution is utilized.
	\item The number of samples is dynamically determined
	      based on the estimated accuracy without the need for predefining it.
\end{itemize}

@@

@@

\subsection{Qualitative Evaluation}
\subsubsection{Experimental Setup}\label{sec:exp_setting}
{%
	\renewcommand{\arraystretch}{1.05}
	\begin{table}[tbp]
		\centering
		\caption{%
			Attributes of the recidivism dataset used in the experiments.
			Continuous features are all discretized
			and only binary and ordinal features are considered.
		}\label{tab:rcdv}
		\begin{tabular}{llc}
			\toprule
			Attribute              & Overview                              & \# of Possible Values \\
			\midrule
			Race                   & Race (Black or White)                 & 2                     \\
			Alcohol                & Presence of serious alcohol issues    & 2                     \\
			Junky                  & Drug usage                            & 2                     \\
			Supervised Release     & Supervised release                    & 2                     \\
			Married                & Marital status                        & 2                     \\
			Felony                 & Felony or not                         & 2                     \\
			WorkRelease            & Participation in work release program & 2                     \\
			Crime against Property & Crime against property or not         & 2                     \\
			Crime against Person   & Crime against a person or not         & 2                     \\
			Gender                 & Gender (Female or Male)               & 2                     \\
			Priors                 & Number of prior offenses              & 4                     \\
			YearsSchool            & Years of formal education completed   & 4                     \\
			PrisonViolations       & Number of prison rule violations      & 3                     \\
			Age                    & Age                                   & 4                     \\
			MonthsServed           & Months served in prison               & 4                     \\
			\midrule
			Recidivism             & Recidivism or not                     & 2                     \\
			\bottomrule
		\end{tabular}
	\end{table}
}

The experiments utilized the recidivism dataset \cite{schmidt1988predicting}.
This dataset contains information on 9,549 prisoners released from
North Carolina prisons between July 1, 1979, and June 30, 1980.
The dataset includes 19 items such as race, gender,
presence of alcohol dependence, number of prior offenses, and recidivism.
For this experiment,
we treated the binary classification problem of predicting
the presence or absence of recidivism (Recidivism) as the target label.
We discretized continuous features and removed missing values,
resulting in 15 features.
This problem setting can be considered as a case
where a machine learning model is introduced to decide parole for prisoners.
Since such decisions can have a significant impact on a person's life,
it is crucial for users to interpret the outputs of black-box models appropriately.

@@

\section{Challenges and Future Perspectives}
 {%
  \def\imgwidth{0.49\textwidth}
  \begin{figure}[t]
	  \centering
	  \begin{subfigure}[t]{\imgwidth}
		  \centering
		  \includegraphics[width=0.78\textwidth]{newlime}
		  \caption{R-LIME for balanced data.}\label{fig:balanced}
	  \end{subfigure}
	  \begin{subfigure}[t]{\imgwidth}
		  \centering
		  \includegraphics[width=0.8\textwidth]{newlime_for_imbalanced_data}
		  \caption{R-LIME for imbalanced data.
		  }\label{fig:imbalanced}
	  \end{subfigure}
	  \caption{%
		  Behavior of R-LIME for balanced and imbalanced data.
		  In case of imbalanced label distribution,
		  the approximation region covers the entire input space and the
		  linear approximation model always outputs the majority label.
	  }
	  \vspace{10pt}
  \end{figure}
 }

\subsection{Computational Complexity}
Most post-hoc explanation methods, including LIME, Anchor, BELLA and R-LIME,
need to query the black-box model multiple times
to get labels for perturbed samples, which can be computationally expensive.
The number of queries required for LIME is $|\mathcal{Z}_p|$,
where $|\mathcal{Z}_p|$ is the number of perturbed samples.

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\newpage
\bibliographystyle{splncs04}
\bibliography{MyRef/ref}
%
\end{document}

>>>>

% settings for cleveref
\crefname{figure}{Fig.}{Figs.}
\crefname{table}{Table}{Tables}
\crefname{algorithm}{Algorithm}{Algorithms}

@@

\section{Introduction}
Machine learning models, such as deep learning and random forests,
have been widely employed in various industrial applications
due to their significant improvement in accuracy in recent years.
However,
the increasing complexity and black-box nature of these models pose challenges,
particularly in critical decision-making scenarios like healthcare and finance,
where the opacity of decision process becomes a major obstacle to
implementation.
Consequently,
there has been extensive research in the field of post-hoc explanations
for machine learning models~\cite{%
	guidotti2018local,radulovic2023bella,ribeiro2016why,ribeiro2018anchors}.
Existing post-hoc explanation methods are categorized
into \emph{model-dependent} and \emph{model-agnostic} methods
based on their dependence on the model's structure.
Furthermore, model-agnostic methods are classified into
\emph{global} and \emph{local} methods based on their locality in input space.

This paper specifically focuses
on \emph{model-agnostic} and \emph{local} methods,
which do not rely on the models' structure
and explain the models' behavior
in the vicinity of a given input (focal point).
For example, LIME (Local Interpretable Model-agnostic Explanations)
\cite{ribeiro2016why} approximates the complex model's decision boundary
locally using a simpler model around the given focal point.
Although LIME enables users to interpret the local behavior of complex models,
it does not explicitly provide the effective scope of the explanation
\cite{ribeiro2018anchors}.
This limitation can lead
users to overgeneralize the knowledge derived from the explanation.
Without a clear indication of the scope of the explanation,
users might mistakenly apply
the derived knowledge to instances outside this scope,
potentially leading to misunderstanding of the black-box model's behavior.

To address this limitation of LIME,
we propose a new method called R-LIME (Ruled LIME),
which interprets complex classifiers in an interpretable region.
R-LIME locally approximates a complex decision boundary linearly
in a rectangular region and maximizes the region
as long as the accuracy of the linear classifier is
higher than a given threshold.
The resulting rectangular region is interpretable for users because it is
expressed as a conjunction of feature predicates (\cref{fig:example-rlime}).

\section{Related Work}
In this chapter,
we overview existing research on post-hoc explanations,
which explain the behavior of complex models already trained.
They are categorized
into \emph{model-dependent} and \emph{model-agnostic} methods
based on their dependence on the model's structure.

Model-dependent methods,
such as DTD (Deep Taylor Decomposition)~\cite{montavon2017explaining}
and LRP (Layer-wise Relevance Propagation)~\cite{bach2015pixel},
primarily focus on deep neural networks and
explain the models' behavior using their parameters~\cite{samek2021explaining}.
While these methods can provide detailed explanations
(e.g., layer-wise explanations for neural networks)
using the models' internal parameters,
it is often challenging
to apply the same method to models with different structures.

On the other hand,
model-agnostic methods
do not rely on the models' parameters and utilize only their output.
Although these methods are applicable to any model,
they cannot explain the reasoning process inside the model.
Furthermore, model-agnostic methods are classified into
\emph{global} and \emph{local} methods based on their locality in input space.
Global methods,
such as PDP (Partial Dependence Plots)~\cite{friedman2001greedy}
and ALE (Accumulated Local Effects)~\cite{apley2020visualizing},
aim to explain the model's behavior across the entire input space,
seeking explanations valid for any input.
However, providing global explanations becomes challenging
as the model's complexity increases.
In contrast, local methods,
such as LIME (Local Interpretable Model-agnostic Explanations)~\cite{ribeiro2016why}
and Anchor~\cite{ribeiro2018anchors},
% SHAP~\cite{lundberg2017unified},
% EXPLAN~\cite{rasouli2020explan},
% LORE (Local Rule-based Explanations)~\cite{guidotti2018local}
% and BELLA (Black box model Explanations by Local Linear Approximations)
% \cite{radulovic2023bella},
explain output of the model for a specific input
(focal point) in the vicinity of that input.
While local methods offer more simple and accurate explanations
than global methods,
the scope of the explanation is limited to the vicinity of the focal point.

\begin{figure}[tbp]
	\def\scale{0.38}
	\centering
	\vspace{0.5cm}
	\begin{subfigure}[t]{0.55\textwidth}
		\centering
		\includegraphics[scale=\scale]{example-instance}
		\caption{Focal point.}\label{fig:example-instance}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{0.45\textwidth}
		\begin{subfigure}[t]{\textwidth}
			\centering
			\includegraphics[scale=\scale]{example-lime}
			\caption{%
				Explanation by LIME\@.
				It provides contributions of each feature to the output,
				but does not explicitly indicate its scope.
			}\label{fig:example-lime}
			\vspace{0.4cm}
		\end{subfigure}
		\begin{subfigure}[t]{\textwidth}
			\centering
			\includegraphics[scale=\scale]{example-anchor}
			\caption{%
				Explanation by Anchor.
				It provides the effective scope of the explanation,
				but does not show the influence of each feature.
			}\label{fig:example-anchor}
		\end{subfigure}
	\end{subfigure}
	\hspace{0.3cm}
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\vspace{-2.24cm}
		\includegraphics[scale=\scale]{example-rlime}
		\caption{%
			Explanation by R-LIME\@.
			It provides both contributions of each feature and
			its effective scope.
		}\label{fig:example-rlime}
	\end{subfigure}
	\caption{%
		Example of explanations by LIME~\cite{ribeiro2016why},
		Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method).
		for a sentiment prediction model.
	}\label{fig:example}
\end{figure}
In this paper,
we focus on local model-agnostic methods.
An example of explanations by LIME and Anchor
for a sentiment prediction model is illustrated in \cref{fig:example}.
LIME~\cite{ribeiro2016why} approximates the complex decision boundary
locally using a linear model around the given focal point,
then provides the weights of the linear model as the contribution of each feature
to the output.
The explanation by LIME (\cref{fig:example-lime}) provides suggests that
the word ``not'' mainly contributes to the positive prediction,
but does not explicitly indicate the effective scope.
Without the scope,
users might mistakenly apply the knowledge derived from the explanation
to other instances far from the focal point,
potentially leading to misunderstanding of the black-box model's behavior
\cite{ribeiro2018anchors}.
For example,
user may apply the insights derived from the explanation
to the sentence ``This book is not good.''
and mistakenly conclude that the word ``not''
mainly contributes to the positive prediction for this sentence as well,
which is incorrect obviously.
Anchor~\cite{ribeiro2018anchors} represents a rectangular region
containing the focal point,
that maximizes the probability of the black-box classifier outputting
the same label as the focal point.
While Anchor provides an effective scope of the explanation,
the information it includes is less than LIME,
limiting its utility~\cite{ribeiro2018anchors}.
The explanation by Anchor (\cref{fig:example-anchor})
suggests that changing words other than ``not'' and ``bad''
has little impact on the classifier's output.
While it clearly cannot be applied to the sentence ``This book is not good''
because of not including the word ``bad'',
the explanation does not provide details about the influence of each word,
resulting in less user insight into the model's behavior compared to LIME.

@@

LIME provides valuable insights into the local behavior of the model
by showing the contribution of each feature to the output $f(x)$.
However, due to not explicitly indicating the perturbation region,
users cannot assess the effective scope of the explanation
\cite{ribeiro2018anchors}.

@@

\subsection{Overview}
We propose R-LIME,
a method that aims to address the limitations of LIME~\cite{ribeiro2016why},
and Anchor~\cite{ribeiro2018anchors}.
Our method locally approximates the given black-box classifier $f$
around the focal point $x$ by a linear classifier $g$ similar to LIME and BELLA,
but samples perturbation from a rectangular region similar to Anchor
so that the generality of approximation is explicitly provided
(\cref{fig:rlime}).
The accuracy of $g$ is defined as the "accuracy" of the rule,
and the generality of explanations is defined as the "coverage" of the rule.

Anchor maximizes the coverage of region $A$
as long as the probability of the output of the black-box classifier $f$ matching $f(x)$
within $A$ exceeds a given threshold $\tau$.
The proposed method, on the other hand, learns an linear classifier $g$
within the rectangular region $A$ and maximizes the coverage of $A$
under lower constraints on the accuracy of $g$.
We modify the Anchor's definition of accuracy in \cref{eq:anchor_def_prec}
as follows:
\begin{equation}
	\Prec(A)=\underset{g\in G}{\max}\ \mathbb{E}_{z\sim\mathcal{D}(z|A)}
	[\mathbbm{1}_{f(z)=g(z)}]. \label{eq:def_prec}
\end{equation}
where $G$ is the set of possible linear classifiers.
By solving the optimization problem in \cref{eq:main_problem}
under the modified accuracy definition in \cref{eq:def_prec},
we can select the rule that enables explanation with high accuracy and generality.
% The characteristics of R-LIME are listed below:
% \begin{itemize}
% 	\item The approximation region is optimal and interpretable.
% 	\item The dataset is not directly accessed, and only the distribution is utilized.
% 	\item The number of samples is dynamically determined
% 	      based on the estimated accuracy without the need for predefining it.
% \end{itemize}

@@

\subsection{Computational Complexity}
Post-hoc explanation methods including LIME, Anchor, and R-LIME
need to query the black-box model multiple times
to get labels for perturbed samples, which is computationally expensive.
The number of queries required for LIME is $|\mathcal{Z}_p|$,
where $|\mathcal{Z}_p|$ is the number of perturbed samples.
On the other hand, the number of queries required for Anchor and R-LIME
is $|\mathcal{D}|$,

@@

\subsection{Qualitative Evaluation}
\subsubsection{Experimental Setup}\label{sec:exp_setting}
{%
	\renewcommand{\arraystretch}{1.05}
	\begin{table}[tbp]
		\centering
		\caption{%
			Attributes of the recidivism dataset used in the experiments.
			Continuous features are all discretized,
			and only binary and ordinal features are considered.
		}\label{tab:rcdv}
		\begin{tabular}{llc}
			\toprule
			Attribute              & Overview                              & \# of Possible Values \\
			\midrule
			Race                   & Race (Black or White)                 & 2                     \\
			Alcohol                & Presence of serious alcohol issues    & 2                     \\
			Junky                  & Drug usage                            & 2                     \\
			Supervised Release     & Supervised release                    & 2                     \\
			Married                & Marital status                        & 2                     \\
			Felony                 & Felony or not                         & 2                     \\
			WorkRelease            & Participation in work release program & 2                     \\
			Crime against Property & Crime against property or not         & 2                     \\
			Crime against Person   & Crime against a person or not         & 2                     \\
			Gender                 & Gender (Female or Male)               & 2                     \\
			Priors                 & Number of prior offenses              & 4                     \\
			YearsSchool            & Years of formal education completed   & 4                     \\
			PrisonViolations       & Number of prison rule violations      & 3                     \\
			Age                    & Age                                   & 4                     \\
			MonthsServed           & Months served in prison               & 4                     \\
			\midrule
			Recidivism             & Recidivism or not                     & 2                     \\
			\bottomrule
		\end{tabular}
	\end{table}
}

The experiments utilized the recidivism dataset \cite{schmidt1988predicting}.
This dataset contains information on 9,549 prisoners released from
North Carolina prisons between July 1, 1979, and June 30, 1980.
The dataset includes 19 items such as race, gender,
presence of alcohol dependence, number of prior offenses and recidivism.
For this experiment,
we treated the binary classification problem of predicting
the presence or absence of recidivism (Recidivism) as the target label.
We discretized continuous features and removed missing values,
resulting in 15 features.
This problem setting can be considered as a case
where a machine learning model is introduced to decide parole for prisoners.
Since such decisions can have a significant impact on a person's life,
it is crucial for users to interpret the outputs of black-box models appropriately.

@@

\section{Challenges and Future Perspectives}
 {%
  \def\imgwidth{0.49\textwidth}
  \def\scale{0.08}
  \begin{figure}[t]
	  \centering
	  \begin{subfigure}[t]{\imgwidth}
		  \centering
		  \includegraphics[scale=\scale]{newlime}
		  \caption{R-LIME for balanced label distribution.}\label{fig:balanced}
	  \end{subfigure}
	  \begin{subfigure}[t]{\imgwidth}
		  \centering
		  \includegraphics[scale=\scale]{newlime_for_imbalanced_data}
		  \caption{R-LIME for imbalanced label distribution.
		  }\label{fig:imbalanced}
	  \end{subfigure}
	  \caption{%
		  Behavior of R-LIME for balanced and imbalanced label distribution.
		  In case of imbalanced label distribution,
		  the approximation region covers the entire input space and the
		  linear approximation model always outputs the majority label.
	  }
  \end{figure}
 }

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{MyRef/ref}
%
\end{document}
